PK object batch mode trial

### 2023-09-08 data-raw/batchMode_trial_gpm.Rmd
Starting some code optimizations (avoiding redundancy)

mvbutils::foodweb(where = asNamespace("invivoPKfit"),
                  prune = "get_tkstats",
                  # descendents = FALSE,
                  ancestors = FALSE,
                  border = TRUE, cex = 1, lwd = 1.5)

>>>>

mvbutils::foodweb(where = asNamespace("invivoPKfit"),
                  prune = "transformed_params_2comp",
                  # descendents = FALSE,
                  # ancestors = FALSE,
                  border = TRUE, cex = 1, lwd = 1.5)
